---
title: "week 6"
author: "Roshni Katrak-Adefowora"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

## Rank-based test example (Mann-Whitney U)

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size=15, replace=TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size=15, replace=TRUE)

hist(gp_2)
```
Reasons to use a rank-based test:
1. Not clearly normally distributed from exploratory histograms
2. Somewhat small sample size (n = 15 for each)
3. I’ve decided that ranks (or, medians) are a more valuable metric to compare for these data.

Mann-Whitney U
Is there a significant difference in ranks (medians) between gp_1 and gp_2?
```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
```
## Simple Linear Regression

### A. Look at the data!
```{r}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g))+
  geom_point()
```

Ask:
1. Does it look like a linear relationship makes sense?
2. Do we have any concerns about modeling as a linear relationship?
3. Any notable outliers?
4. Initial thoughts about homoscedasticity (explored more later)?

### B. Model it

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data=penguins)
summary(penguin_lm)
```

### C. Access model outputs

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm) #tidy, dataframe output

#get intercept
penguin_int <- penguin_lm_tidy$estimate[1]

#get flipper length coefficient
penguin_coef <- penguin_lm_tidy$estimate[2]

#metrics at a glance
penguin_lm_out <- broom::glance(penguin_lm)
penguin_lm_out
```

### D. Explore model assumptions

```{r}
plot(penguin_lm)
```

### E. Visualize the model

```{r}
ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g))+
  geom_point(size=2)+
  geom_smooth(method="lm",
              color="red",
              size=0.5,
              fill="gray10",
              alpha=0.5)+
  theme_light()+
  ggpubr::stat_regline_equation(label.x=180, label.y=5700)
```

### F. Find Pearson's *r* for correlation

```{r}
penguins_cor <- cor.test(penguins$flipper_length_mm, penguins$body_mass_g)
penguins_cor
```

